Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
svg

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	%\vspace{-2.0em}
	\caption{
		%
		Comparison in Robustness, Training Cost, and Recall@1 Performance
		between Our Method (\ie, ``HM'') and the State-of-The-Art Method (\ie, ``ACT'').
		%
		Best viewed in color.
	}
	\label{fig:introplot}
\end{figure}

>>>>

\begin{figure}[t]
	\includegraphics[width=1.0\columnwidth]{introplot.pdf}
	%\vspace{-2.0em}
	\caption{
		%
		Comparison in Robustness, Training Cost, and Recall@1 Performance
		between Our Method (\ie, ``HM[$\mathcal{S},g_\mathsf{SGA}$]\&ICS'')
		and the State-of-The-Art Method (\ie, ``ACT[$\mathcal{R}$]'' and
		``ACT[$\mathcal{S}$]'').
		%
	}
	\label{fig:introplot}
\end{figure}
